---
title: "Lab9"
author: "Yingtong Lyu"
date: "November 12, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "Lab9"
author: "Yingtong Lyu"
date: "November 12, 2018"
output: pdf_document
---


##1. Consider a function that counts number of odd numbers in a given vector
```{r}
odd_count = function(x){
  odd_num = 0
  for (i in 1:length(x)){
    if (x[i] %% 2 ==1) odd_num = odd_num+1
  }
  return(odd_num)
}
```

Write a vectorized form of this function and compare their performance using microbenchmark function from the package microbenchmark
```{r}
library(microbenchmark)
library(profvis)
```

```{r}
odd_count2 <- function(x){
  sum(x %% 2 ==1)
  #sum(ifelse(x %% 2==1,yes=1,no=0))
}
x <- c(1:100)
microbenchmark(odd_count(x),odd_count2(x))
```
#2. Modify the sorting function (sort_vec) from "Assignment 8" (problem 3) so that it should take an additional argument ascending which causes sorting in increasing order when 'ascending = TRUE'. In other words,
. sort_vect(c(3, 1, 2), ascending = TRUE) = (1, 2, 3)
. sort_vect(c(3, 1, 2), ascending = FALSE) = (3, 2, 1)

```{r}
sort_vec = function(x, ascending = TRUE) {
    
  if (length(x) < 2) 
    return (x)
  
  for(last in length(x):2) {
    for(first in 1:(last - 1)) {
      
      if (ascending ==TRUE){
        
      if(x[first] > x[first + 1]) {
        temp <- x[first]
        x[first] <- x[first + 1]
        x[first + 1] <- temp
      }
      }
      
  else {
      if(x[first] < x[first + 1]) {
        temp <- x[first]
        x[first] <- x[first + 1]
        x[first + 1] <- temp
      }
    }
    }
  }
    return(x)
}
sort_vec(c(3, 1, 2), ascending = TRUE)
sort_vec(c(3, 1, 2), ascending = FALSE)

```


#3. Consider a simple random walk with starting point 0 and a step -1 or 1. Below is the code with dynamically allocated memory. Write your code with preallocated memory and compare time for both versions using system.time() function (use N = 1000, 10000 and 1000000).
```{r}
N = 1000
data_series = 0
system.time({for (i in 2:N){
data_series[i] = data_series[i-1] + sample(c(-1, 1), 1)
}
})

```

```{r}
paste0("N=1000")
paste0("dynamically allocated memory")
N = 1000
data_series = 0 
system.time({
  for (i in 2:N){
    data_series[i] = data_series[i-1] + sample(c(-1, 1), 1) 
  }
})
paste0("preallocated memory")
N = 1000
data_series <- vector(length = N)
system.time({
  for (i in 2:N){
    data_series[i] = data_series[i-1] + sample(c(-1, 1), 1) 
  }
})

paste0("N=10000")
paste0("dynamically allocated memory")
N = 10000
data_series = 0 
system.time({
  for (i in 2:N){
    data_series[i] = data_series[i-1] + sample(c(-1, 1), 1) 
  }
})
paste0("preallocated memory")
N = 10000
data_series <- vector(length = N)
system.time({
  for (i in 2:N){
    data_series[i] = data_series[i-1] + sample(c(-1, 1), 1) 
  }
})

paste0("N=1000000")
paste0("dynamically allocated memory")
N = 1000000
data_series = 0 
system.time({
  for (i in 2:N){
    data_series[i] = data_series[i-1] + sample(c(-1, 1), 1) 
  }
})
paste0("preallocated memory")
N = 1000000
data_series <- vector(length = N)
system.time({
  for (i in 2:N){
    data_series[i] = data_series[i-1] + sample(c(-1, 1), 1) 
  }
})
```

